DOpElib - Deal Optimization Environment

### 2012-03-16 Examples/Documentation/examples.tex
Augmented the Documentation. Please read carefully to see if this is fine

Adding a new regression test to the repository 
needs some concentration of the user. In the 
following, we explain how to do this and what 
\textit{must} be taken into account:
\begin{verbatim}
cp -r Example1 ExampleNew
cd ExampleNew
rm -r CVS
cd Test
rm -r CVS
\end{verbatim}
It is important to remove the repository information,
which is stored in the directory CVS.

>>>>

Adding a new regression test to the repository 
needs some concentration of the user. In the 
following, we explain how to do this and what 
\textit{must} be taken into account:
\begin{verbatim}
cp -r Example1 ExampleNew
cd ExampleNew
rm -rf .svn
cd Test
rm -rf .svn
\end{verbatim}
It is important to remove the repository information,
which is stored in the directory .svn.

### 2012-03-16 Examples/Documentation/foreword.tex
Augmented the Documentation. Please read carefully to see if this is fine

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \textit{Deal Optimization Environment} (DOpE) project is 
based on the \textit{deal.II} finite element library which has been developed
 initially by W. Bangerth, R. Hartmann, and G. Kanschat. \marginpar{Citation}
Its main feature is to give a unified interface to highlevel algorithms such as 
time stepping methods, nonlinear solvers and optimization routines. 
We aim that the user should only need to write those parts
of the code that are problem dependent while all invariant parts of the algorithms
should be reusable without any need for further coding.
In particular, the user should be able to switch between various different 
algorithms without the need to rewrite the problem dependent code, though he or she will
have to replace the algorithm object with an other one.

The authors acknwoledge their past experience as well as discussions with 
the authors of the libraries 
Gascoigne/RoDoBo project, which was initiated by 
Roland Becker, Dominik Meidner,  and Boris Vexler. \marginpar{Citation} 
From which some of the ideas to modularize the algorithms have arisen.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
At the present stage the following features are supported by the library
\begin{itemize}
\item Solution of stationary and nonstationary PDEs in 1d, 2d, and 3d.
\item Various timestepping schemes (based on finite differences), 
  such as forward Euler, backward Euler,
  Crank-Nicolson, shifted Crank-Nicolson, and Fractional-Step-$\Theta$ scheme.
\item All finite elements of from deal.ii including hp-support.
\item Several examples showing the solution of several PDEs including
   Poisson, Navier-Stokes, Plasticity and fluid-structure interaction problems. 
\item Self written linesearch and trustregion newton algorithms for the 
   solution of optimization problems with PDEs. (cp. Nocedal \& Wright\marginpar{Citation})
\item Interface to SNOPT for the solution of optimization problems with PDEs and
  additional other constraints.
\item Several examples showing how to solve various kinds of optimization problems
  involving stationary PDE constraints.
\item Mesh adaptation.
\item Different spatial triangulations for control and state variables.
\end{itemize}

@@

Then assuming that you can work to your satisfaction with the algorithms already implemented
we will show you how to create your own running example in Chapter~\ref{chap:howtoex}.
This will be followed by a detailed description of all examples already shipped with 
the library. You can find the examples for the solution of PDEs in Chaper~\ref{PDE}
and those for the solution of optimization problems with PDEs in Chapter~\ref{OPT}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \textit{Deal Optimization Environment} (DOpE) project is 
based on the \textit{deal.II} finite element library which has been developed
 initially by W. Bangerth, R. Hartmann, and G. Kanschat. \marginpar{Citation}
Its main feature is to give a unified interface to high level algorithms such as 
time stepping methods, nonlinear solvers and optimization routines. 
We aim that the user should only need to write those parts
of the code that are problem dependent while all invariant parts of the algorithms
should be reusable without any need for further coding.
In particular, the user should be able to switch between various different 
algorithms without the need to rewrite the problem dependent code, though he or she will
have to replace the algorithm object with an other one.

The authors acknowledge their past experience as well as discussions with 
the authors of the libraries 
Gascoigne/RoDoBo project, which was initiated by 
Roland Becker, Dominik Meidner,  and Boris Vexler. \marginpar{Citation} 
From which some of the ideas to modularize the algorithms have arisen.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
At the present stage the following features are supported by the library
\begin{itemize}
\item Solution of stationary and nonstationary PDEs in 1d, 2d, and 3d.
\item Various time stepping schemes (based on finite differences), 
  such as forward Euler, backward Euler,
  Crank-Nicolson, shifted Crank-Nicolson, and Fractional-Step-$\Theta$ scheme.
\item All finite elements of from deal.ii including hp-support.
\item Several examples showing the solution of several PDEs including
   Poisson, Navier-Stokes, Plasticity and fluid-structure interaction problems. 
\item Self written line search and trust region newton algorithms for the 
   solution of optimization problems with PDEs. (cf. Nocedal \& Wright\marginpar{Citation})
\item Interface to SNOPT for the solution of optimization problems with PDEs and
  additional other constraints.
\item Several examples showing how to solve various kinds of optimization problems
  involving stationary PDE constraints.
\item Mesh adaptation.
\item Different spatial triangulations for control and state variables.
\end{itemize}

@@

Then assuming that you can work to your satisfaction with the algorithms already implemented
we will show you how to create your own running example in Chapter~\ref{chap:howtoex}.
This will be followed by a detailed description of all examples already shipped with 
the library. You can find the examples for the solution of PDEs in Chapter~\ref{PDE}
and those for the solution of optimization problems with PDEs in Chapter~\ref{OPT}.

### 2012-03-16 Examples/Documentation/introduction.tex
Augmented the Documentation. Please read carefully to see if this is fine

\section{Software requirements}

@@

The deal.II library is open source and is freely availiable for noncommercial project.
It can be downloaded from \url{http://www.dealii.org/}. On this
homepage, one also finds lots of further information on deal.II as well as
an extensive tutorial where many features of deal.II are discussed in a
well-documented example framework. In order to use DOpE, it is highly
recommendable to be roughly acquainted with deal.II.

\subsection{SNOPT}
If you would like to use the features offered in our SNOPT wrapper. You will 
need to obtain a licence for {\tt SNOPT} 
\url{http://www.sbsi-sol-optimize.com/asp/sol_product_snopt.htm}.
Unfortuately this is at present not availiable for free, but you should check if 
there is a department license already availiable.

\section{How this library is struktured}
\marginpar{TODO!}

>>>>

\section{Software requirements}
The library DOpE has been tested to work on both Linux and 
MAC OSX. It requires a recent {\tt g++} (at least 4.4.3) due to 
some new {\tt C++} features implemented in {\tt C++0x} and {\tt C++11}.

@@

The deal.II library is open source and is freely available for noncommercial project.
It can be downloaded from \url{http://www.dealii.org/}. On this
homepage, one also finds lots of further information on deal.II as well as
an extensive tutorial where many features of deal.II are discussed in a
well-documented example framework. In order to use DOpE, it is highly
recommendable to be roughly acquainted with deal.II.

\subsection{SNOPT}
If you would like to use the features offered in our SNOPT wrapper. You will 
need to obtain a license for {\tt SNOPT} 
\url{http://www.sbsi-sol-optimize.com/asp/sol_product_snopt.htm}.
Unfortunately this is at present not available for free, but you should 
check if 
there is a department license already available.

\section{How this library is structured}
This library is designed to allow easy implementation and numerical solutions 
of problems involving partial differential equations (PDEs). The easiest case 
is that of a PDE in weak form to find some $u$
\[
a(u)(\phi) = 0 \quad \forall \phi \in V
\]
with some appropriate space $V$.
More complex cases involve optimization problems given in the form (OPT)
\begin{align*}
\min\;&J(q,u) \\
  &\text{s.t.}\; a(q,u) = 0 \quad \forall \phi\\
  &a \le q \le b\\
  &g(q,u) \le 0  
\end{align*}
where $u$ is a FE-function and $q$ can either be a FE-function or some 
fixed number of parameters.

\subsection{Problem description}
In order to allow our algorithms the automatic assembly of all required 
data we need to have some container which contains the complete problem 
description in a common data format. For this we have the following 
classes in {\tt DOpEsrc/container}
\begin{itemize}
  \item {\tt pdeproblemcontainer.h} Is used to describe  stationary PDE problems.
  \item {\tt instatpdeproblemcontainer.h} {\bf TODO is still missing but will be used for nonstationary problems.} This will be implemented once we have nonstationary optimization problems running to avoid error duplication in the coding process.
  \item {\tt optproblem.h} Is used to describe  OPT problems governed by 
    stationary PDEs. {\bf TODO should be renamed to optproblemcontainer.h including the class name!}
  \item {\tt instatoptproblemcontainer.h} Is used to describe  OPT problems governed by nonstationary PDEs. The only difference to the stationary case is that we need to specify a time-stepping method.  
\end{itemize}
In order to fill these containers there are two things to be done,
first we need to actually write some data like $a$, $J$, $\ldots$
which describe the problem. Then we have to select some numerical 
algorithm components like finite elements, linear solvers $\ldots$.
The latter ones should be written such that when exchanging these components
none of the problem descriptions should require changes. 
Note that it still may be necessary to write some additional descriptions, 
e.g., if you solve the PDE with a fix point iteration you don't need derivatives
but if you want to use Newton's method you then have to provide some.

We will start by discussing the problem description components implemented so far

\subsubsection{Problem specific classes}
The following classes are used to describe the problem and will usually require 
some implementation.

\begin{itemize}
  \item {\tt basic/constraints.h} This is used by the spacetimehandlers to 
    compute the number of constraints from the control and state vectors. 
    It must not be reimplemented by the user, but needs to be properly 
    initialized if OPT is used with box control constraints or $g(q,u) \le 0$.
  \item {\tt interfaces/functionalinterface.h} This gives an interface 
    for the functional $J$ and any other functional you may want to evaluate.
    In general this can be used as a base class to write your own functionals 
    in examples. We note that we only need to write the integrands on 
    elements or faces the loop over elements will be taken care of else where.
  \item {\tt interfaces/constraintinterface.h} This gives an interface for both 
    the control box constraints as well as the general constraint $g \le 0$. This 
    needs to be specified if constraints are to be used. If they are not needed 
    a default class {\tt problemdata/noconstraints.h} can be used. We note that we only 
    need to write the integrands on 
    elements or faces the loop over elements will be taken care of else where.
  \item {\tt interfaces/pdeinterface.h} This defines an interface for the 
    partial differential equation $a(q,u)(\phi) = 0$. This needs to be written
    by the user. We note that we only need to write the integrands on 
    elements or faces the loop over elements will be taken care of else where.
  \item {\tt interfaces/dirichletdatainterface.h} This gives an interface to the 
    Dirichlet data for a problem. If the Dirichlet data are simply a function 
    (and do not depend on the control $q$ one can use the default class
    {\tt problemdata/simpledirichletdata.h}.
\end{itemize}

\subsubsection{Numeric components}
These are the components from which a user needs to select some in order to actually 
solve the given problem. They will not require any rewriting, but sometimes it is 
advisable to write other than the default parameter into the param file for the 
solution.

First we need to select a method how to handle all dofs in space and time.
\begin{itemize}
\item {\tt basic/spacetimehandler\underline{ }base.h} This class is used to define 
  an interface to the dimension independent functionality of all space time dof handlers. 
\item {\tt basic/statespacetimehandler.h} Another intermediate interface class which adds 
  the dimension dependent functionality if only the variable $u$ is considered, i.e., a 
  PDE problem.
\item {\tt basic/spacetimehandler.h } Same as above but with both $q$ and $u$, i.e., for
  OPT problems.
\item {\tt basic/mol\underline{ }statespacetimehandler.h} Implementation of a method of 
  line space time dof handler for PDE problems. It has only one spatial 
  dofhandler which is used for all time intervals.
\item {\tt basic/mol\underline{ }spacetimehandler.h} Same as above for OPT problems.
  A separate spatial dof handler for each of the variables $q$ and $u$ is maintained 
  but only one triangulation.
\item {\tt basic/mol\underline{ }multimesh\underline{ }spacetimehandler.h}
  Same as above, but now in addition the triangulations for $q$ and $u$ can be refined
  separately from one common initial coarse triangulation. Note that this will
  in addition require the use of the multimesh version for integrator and 
  face- as well as celldatacontainer.
\end{itemize}
Note that we use these for stationary problems as well, but then you don't have to specify
any time information.

Second you will need to specify some container classes to be used to 
pass data between objects. At present you don't have much choice, but you may wish 
to reimplement some of these if you need data that is not currently included in 
the containers.
\begin{itemize}
\item {\tt container/celldatacontainer.h} This object is used to pass data 
  given on the current element (cell) of the mesh to the functions in PDE, functional, 
  $\ldots$. 
\item {\tt container/facedatacontainer.h} This object is used to pass data 
  given on the current face of the mesh to the functions in PDE, functional, 
  $\ldots$. 
\item {\tt container/multimesh\underline{ }celldatacontainer.h} This is the same as the 
  celldatacontainer, but it
  is capable to handle data defined on an alternative triangulation.
\item {\tt container/multimesh\underline{ }facedatacontainer.h} This is the same as the
  facedatacontainer, but it
  is capable to handle data defined on an alternative triangulation.
\item {\tt container/integratordatacontainer.h} This contains some data that 
  should be passed to the integrator like quadrature formulas and the above cell and 
  face data container.
\end{itemize}

Third, at least for nonstationary PDEs we need to select a time stepping scheme
the file names of which are mostly self explanatory:
\begin{itemize}
\item {\tt include/forward\underline{ }euler\underline{ }problem.h}
\item {\tt include/shifted\underline{ }crank\underline{ }nicolson\underline{ }problem.h}
\item {\tt include/backward\underline{ }euler\underline{ }problem.h}
\item {\tt include/fractional\underline{ }step\underline{ }theta\underline{ }problem.h} Note that the use of this scheme requires a special Newton solver!
\item {\tt include/crank\underline{ }nicolson\underline{ }problem.h}
\end{itemize}

Finally, we need to select a way how to integrate and solve linear and nonlinear equations
\begin{itemize}
\item {\tt templates/integrator.h} This class computes integrals over a given 
  triangulation (including its faces).
\item {\tt templates/integrator\underline{ }multimesh.h} The same as above but it is 
  possible that some of the FE functions are defined on an other triangulation 
  as long as the have a common coarse triangulation.
\item {\tt templates/integratormixeddims.h} This is used to compute integral which 
  are given in another (larger) dimension than the current variable. (This is exclusively
  used if the control variable is given by some parameters. Which means {\tt dopedim == 0}). 
\item {\tt templates/cglinearsolver.h} This is a wrapper for the cg solver implemented in 
  {\tt deal.ii}. The solver will build and store the stiffness matrix for the PDE.
\item {\tt templates/gmreslinearsolver.h} This is a wrapper for the gmres solver 
  implemented in {\tt deal.ii}. The solver will build and store the stiffness matrix 
  for the PDE.
\item {\tt templates/directlinearsolver.h} This is a wrapper for the direct solver 
  implemented in {\tt deal.ii} using {\tt UMFPACK}. 
  The solver will build and store the stiffness matrix for the PDE.
\item {\tt templates/voidlinearsolver.h} This is a wrapper for certain cases when we 
  know that the matrix to be inverted is the identity. It simply copies the rhs to the
  lhs. This is only needed for compatibility reasons some other components.
\item {\tt templates/newtonsolver.h} This solves some nonlinear equation using a 
  line-search Newton method.
\item {\tt templates/newtonsolvermixeddims.h} The same but in the case when there is 
  another variable in a (larger) dimension is involved. See 
  {\tt integratormixeddims.h}.
\item {\tt templates/instat\underline{ }step\underline{ }newtonsolver.h} This is a 
  Newton method as above to invert the next time-step. It differs from the plain vanilla
  version in that it computes certain data from the previous time step only once 
  and not in every Newton iteration.
\item {\tt templates/fractional\underline{ }step\underline{ }theta\underline{ }step\underline{ }newtonsolver.h} This is the Newton solver for the time step in a 
  fractional-step-theta scheme. It combines the computation of all three sub steps.
\end{itemize}

\subsection{Reduced problems (Solve the PDE)}
At times it is nice to remove the PDE constraint. This is handled by so called reduced 
problems. This means that the reduced problem implicitly solves the PDE whenever required
and eliminates the variable $u$ from the problem.
\begin{itemize}
\item {\tt reducedproblems/statpdeproblem.h} This is used to remove the variable $u$ in 
  a stationary PDE problem. This means that call the method \\
  {\tt StatPDEProblem::ComputeReducedFunctionals} will evaluate the functionals 
  defined in the problem description, i.e., in {\tt PDEProblemContainer}, in the 
  solution of the given PDE.
\item {\tt reducedproblems/statreducedproblem.h} This eliminates $u$ from the OPT
  problem with a stationary PDE.
\item {\tt reducedproblems/instatreducedproblem.h} The same as above but for a
  nonstationary PDE. {\bf FIXME there is something wrong in this file see FIXME 
    comment in the source.}
\item {\tt reducedproblems/voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint.
\end{itemize}

\subsection{Optimization algorithms}
Now, in order to solve optimization algorithms we need to define some algorithms.
At present we offer a selection of algorithms that solve the reduced optimization 
problem where the PDE constraint has been eliminated as explained in the previous section
\begin{itemize}
\item {\tt opt\underline{ }algorithms/reducedalgorithm.h} An interface for all 
  optimization problems in the reduced formulation. It offers some test functionality
  to assert that the derivatives of the problem are computed correctly.
\item {\tt opt\underline{ }algorithms/reducednewtonalgorithm.h}
  A line-search Newton algorithm using a cg method to invert the reduced hessian. 
  Implementation ignores any additional constraints.
\item {\tt opt\underline{ }algorithms/reducedtrustregionnewton.h}
  A trust region Newton algorithm using a cg method to invert the reduced hessian.
  Implementation ignores any additional constraints.
\item {\tt opt\underline{ }algorithms/reduced\underline{ }snopt\underline{ }algorithm.h}
  An algorithm to solve reduced optimization problems with additional control constraints.
  ((reduced) state constraints are not yet implemented.)
\item {\tt opt\underline{ }algorithms/reducednewtonalgorithmwithinverse.h}
  Line-search Newton algorithm that assumes there exists a method in the reduced problem
  that can invert the reduced hessian. (This usually makes sense only if there is no 
  PDE constraint.)
\item {\tt opt\underline{ }algorithms/generalized\underline{ }mma\underline{ }algorithm.h}
  An implementation of the MMA-Algorithm for structural optimization using an augmented
  Lagrangian formulation for the subproblems. The subproblem is implemented using the 
  special purpose file
  {\tt include/augmentedlagrangianproblem.h}.
\end{itemize}

\subsection{Other Components}
Beyond these clearly structured groups before there are some classes remaining that
do not fit the above but are important for the user to know:
\begin{itemize}
\item {\tt include/statevector.h} This stores all dofs in space and time for the state 
  variable $u$. It is possible to select whether all this should be kept in memory or 
  or unused parts can be written to the hard disk.
\item {\tt include/controlvector.h} This stores all dofs in space and time for the 
  control variable $q$. At present no time dependence is implemented.
\item {\tt include/constraintvector.h} This stores all dofs in space and time for the 
  non PDE constraints (and corresponding multipliers). 
  At present no time dependence is implemented.
\item {\tt include/parameterreader.h} This file is used to define a parameter reader
  that is used to read run time parameters from a given file.
\item {\tt include/dopeexception.h} Defines some Exceptions that are thrown by the program
  should it encounter any unexpected errors.
\item {\tt include/dopeexceptionhandler.h} This class is used to write information 
  contained in the exceptions to the output in a uniform manner.
\item {\tt include/outputhandler.h} This file defines an outputhandler object which 
  can be used to decide whether some information should be written to screen or file.
  In addition it can format output according to some run time parameters given by a 
  parameter file.
\end{itemize}

\marginpar{Write the rest! WW}
\subsection{Internal structures}
interfaces:
transposeddirichletdatainterface.h
reducedprobleminterface.h
            pdeprobleminterface.h

problemdata:
noconstraints.h        stateproblem.h          transposedgradientdirichletdata.h
primaldirichletdata.h  tangentdirichletdata.h  transposedhessiandirichletdata.h
simpledirichletdata.h
\subsection{Wrapper classes}

wrapper:
dofhandler\underline{ }wrapper.h  finiteelement\underline{ }wrapper.h  preconditioner\underline{ }wrapper.h
fevalues\underline{ }wrapper.h    function\underline{ }wrapper.h       snopt\underline{ }wrapper.h

{\bf TODO! The following files need some appropriate description here 
This should be done by someone who knows what they are used for. Pleas move the description to the right place above.}
\marginpar{TODO}

basic:
      sth\underline{ }internals.h                     
      DOpEtypes.h 
include:   
solutionextractor.h                 
constraintsmaker.h            helloworld.h                     sparsitymaker.h                     
            helper.h                                           timedofhandler.h                    
              timeiterator.h

reducedproblems:
 forwardtimestepreducedproblem.h
interfaces:
active\underline{ }fe\underline{ }index\underline{ }setter\underline{ }interface.h

### 2012-03-16 Examples/Documentation/tests.tex
Augmented the Documentation. Please read carefully to see if this is fine

\chapter{Testing examples}\label{chap:test}
The DOpE testsuite consists of regression tests. They are run to compare 
the output to previous outputs. This is useful (necessary) after 
changing programming code anywhere in the library. If a test
succeeds, everything is fine in the library. If not, you should not
check in your code into DOpE. Please make sure what is going wrong and WHY!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Where can I find the tests}
In each example directory you find a subdirectory `Test'. Herein, you find 
the parameter files for meshes (*.inp) and a param file (test.prm).
Moreover, the executable is denoted by `test.sh'. Please make sure, that 
the 
\begin{verbatim}
set never_write_list
\end{verbatim}
contains every possible output
\begin{verbatim}
Gradient;Hessian;Tangent;Residual;Update;Control;State
\end{verbatim}
That means, no solution files are written to the output.
Recall, that we are just interested in terminal output that 
is of course sufficient to verify the things.

@@

The useful point is now the following. After implemention of 
new pieces of code in the DOpE library or in the examples, you can
run 
\begin{verbatim}
> ./test.sh Test
\end{verbatim}
Hereby, you compare your `new' output with the previous stored output.

>>>>

\chapter{Testing examples}\label{chap:test}
The DOpE test suite consists of regression tests. They are run to compare 
the output to previous outputs. This is useful (necessary) after 
changing programming code anywhere in the library. If a test
succeeds, everything is fine in the library. If not, you should not
check in your code into DOpE. Please make sure what is going wrong and WHY!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Where can I find the tests}
In each example directory you find a sub directory `Test'. Herein, you find 
the parameter files for meshes (*.inp) and a param file (test.prm).
Moreover, the executable is denoted by `test.sh'. Please make sure, that 
the 
\begin{verbatim}
set never_write_list
\end{verbatim}
contains every possible output
\begin{verbatim}
Gradient;Hessian;Tangent;Residual;Update;Control;State
\end{verbatim}
That means, no solution files are written to the output.
Recall, that we are just interested in terminal output that 
is of course sufficient to verify the things.

@@

The useful point is now the following. After implementation of 
new pieces of code in the DOpE library or in the examples, you can
run 
\begin{verbatim}
> ./test.sh Test
\end{verbatim}
Hereby, you compare your `new' output with the previous stored output.

### 2012-03-16 Examples/description.tex
Augmented the Documentation. Please read carefully to see if this is fine

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpE - Deal Optimization Environment}
\author{
  Michael Geiger\thanks{University of Heidelberg, 
    {michael.geiger@iwr.uni-heidelberg.de}}, 
  Christian Goll\thanks{University of Heidelberg, 
    {christian.goll@iwr.uni-heidelberg.de}}, 
  Thomas Wick\thanks{University of Heidelberg, 
    {thomas.wick@iwr.uni-heidelberg.de}}, 
  Winnifried Wollner\thanks{University of Hamburg, 
    {winnifried.wollner@math.uni-hamburg.de}}
}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{DOpElib - Deal Optimization Environment}
\author{
  Christian Goll\thanks{University of Heidelberg, 
    {christian.goll@iwr.uni-heidelberg.de}}, 
  Thomas Wick\thanks{University of Heidelberg, 
    {thomas.wick@iwr.uni-heidelberg.de}}, 
  Winnifried Wollner\thanks{University of Hamburg, 
    {winnifried.wollner@math.uni-hamburg.de}}
}
